---
title: 'Air Quality Analysis 2'
output:
  distill::distill_article:
    toc:false:
      theme: theme.css
---


```{r include = FALSE}
library(tidyverse)
library(olsrr)
library(lmtest)
library(MASS)
library(doParallel)
library(tibble)
library(caret)
library(semPlot)
library(R.utils)
library(glmnet)
library(sampling)
library(treemap)
library(reshape2)
library(dplyr)
library(scales)
library(psych)
library(ggplot2)
library(xlsx)
library(lavaan)
library(emmeans)
library(nlme)
library(lme4)
options(digits = 7)
registerDoParallel()
getDoParWorkers()
```

## Air Quality Analysis Part 2{-}
We have air quality data (NO2, O3, PM25, and PM10) from 2021-03-25 to 2021-12-07 at three different locations (Hine Medical District Drive, Hine Record Crossing, and Inwood UTSW). We want to see if there is any statistical difference between average air quality between 7-10 AM and 4-7 PM.


```{r include = FALSE}
statfunc <-function(location){

print(t.test(x = data_processed$no2_pick[data_processed$SiteName == location], 
       y = data_processed$no2_mor[data_processed$SiteName == location], 
       paired = TRUE, conf.level = 0.95))
printf("\n\n")

print(t.test(x = data_processed$o3_pick[data_processed$SiteName == location], 
       y = data_processed$o3_mor[data_processed$SiteName == location], 
       paired = TRUE, conf.level = 0.95))
printf("\n\n")

print(t.test(x = data_processed$pm25_pick[data_processed$SiteName == location], 
       y = data_processed$pm25_mor[data_processed$SiteName == location], 
       paired = TRUE, conf.level = 0.95))
printf("\n\n")

print(t.test(x = data_processed$pm10_pick[data_processed$SiteName == location], 
       y = data_processed$pm10_mor[data_processed$SiteName == location], 
       paired = TRUE, conf.level = 0.95))
printf("\n\n")

print(t.test(x = data_processed$temp_pick[data_processed$SiteName == location], 
       y = data_processed$temp_mor[data_processed$SiteName == location], 
       paired = TRUE, conf.level = 0.95))
  
}

```

```{r include = FALSE}
data_processed <- read.csv("AQ_processed.csv")
```

## Hines Medical District Drive {-}
There is no statistical difference in NO2, PM25, and PM10 between 7-10 AM and 4-7 PM, while there is a statistical difference in O3 and temperature between 7-10 AM and 4-7 PM.

```{r, echo = FALSE, message=FALSE, warning=FALSE, fig.width=10,fig.height=5, layout="l-body-outset"}
statfunc("Hines_MedicalDistrictDrive")
```
## Hines Record Crossing {-}
There is no statistical difference in NO2, PM25, and PM10 between 7-10 AM and 4-7 PM, while there is a statistical difference in O3 and temperature between 7-10 AM and 4-7 PM.

```{r, echo = FALSE, message=FALSE, warning=FALSE, fig.width=10,fig.height=5, layout="l-body-outset"}
statfunc("Hines_RecordCrossing")
```
## Inwood Crossing {-}
There is no statistical difference in NO2, PM25, and PM10 between 7-10 AM and 4-7 PM, while there is a statistical difference in O3 and temperature between 7-10 AM and 4-7 PM.

```{r, echo = FALSE, message=FALSE, warning=FALSE, fig.width=10,fig.height=5, layout="l-body-outset"}
statfunc("Inwood_UTSW")
```

## Below we want to see if there is any statistical difference between average air quality between 1-3 AM and 4-7 PM.


```{r include = FALSE}
data_processed <- read.csv("AQ_processed V2.csv")
```

## Hines Medical District Drive {-}
There is no statistical difference in PM25 and PM10 between 1-3 AM and 4-7 PM, while there is a statistical difference in O3, NO2, and temperature between 1-3 AM and 4-7 PM.

```{r, echo = FALSE, message=FALSE, warning=FALSE, fig.width=10,fig.height=5, layout="l-body-outset"}
statfunc("Hines_MedicalDistrictDrive")
```
## Hines Record Crossing {-}
There is no statistical difference in PM25 and PM10 between 1-3 AM and 4-7 PM, while there is a statistical difference in O3, NO2, and temperature between 1-3 AM and 4-7 PM.

```{r, echo = FALSE, message=FALSE, warning=FALSE, fig.width=10,fig.height=5, layout="l-body-outset"}
statfunc("Hines_RecordCrossing")
```

## Inwood Crossing {-}
There is no statistical difference in PM25 and PM10 between 1-3 AM and 4-7 PM, while there is a statistical difference in O3, NO2, and temperature between 1-3 AM and 4-7 PM.

```{r, echo = FALSE, message=FALSE, warning=FALSE, fig.width=10,fig.height=5, layout="l-body-outset"}
statfunc("Inwood_UTSW")
```