---
title: "Sensors' Data Dictionary"
output:
  distill::distill_article:
    toc:false:
      theme: theme.css
---

# Hub
The hub receives and processes data from all the different sensors

# MRT Sensor Prototype  
MRT sensor captures air and global temperature. These sensors are located inside a black-painted sphere.

# Light Sensor
Light sensor captures light data. Data from the light sensor is used to differentiate cloudy days from sunny days.   

# TH Sensor 
TH sensor captures temperature and humidity.

# Anemometer 
Anemometer Sensor captures wind speed and direction.   


```{r, MRT Defitions, echo = FALSE, message=FALSE, warning=FALSE, fig.width=12,fig.height=8, layout="l-body-outset"}
order <- c(1, 2, 3, 4)

column_names <- c("timestamp", 
           "air_temp (C)", 
           "GT (C)", 
           "deveui") 

definition <- c("The date and time of each data point are represented every 20 minutes.", 
                "Air temperature is captured and reported in celcius unit.",
                "Global temperature is captured and reported in celcuis unit.",
                "Sensor unique ID")

datadic_def <- data.frame(order, column_names, definition)

tbl_datadic <- reactable(datadic_def,
          compact = TRUE,
          class = "cpal-tbl",
          defaultSorted = c("order"),
          columns = list(
            order = colDef(
              name = "Order",
              show = FALSE),
            column_names = colDef(
              name = "Column Name"),
            definition = colDef(
              name = "Definition")
            ))

div(class = "cpal-table",
  div(class = "cpal-header",
    h2(class = "cpal-title", "Data Dictionary for the MRT Sensor")),
  tbl_datadic
)
```


```{r, TH Defitions, echo = FALSE, message=FALSE, warning=FALSE, fig.width=12,fig.height=8, layout="l-body-outset"}
order <- c(1, 2, 3, 4)

column_names <- c("timestamp", 
           "air_temp (C)", 
           "humidity (%RH)", 
           "deveui") 

definition <- c("The date and time of each data point are represented every 20 minutes.", 
                "Air temperature is captured and reported in celcius unit.",
                "Humidity is captured and reported as relative humidity ratio.",
                "Sensor unique ID")

datadic_def <- data.frame(order, column_names, definition)

tbl_datadic <- reactable(datadic_def,
          compact = TRUE,
          class = "cpal-tbl",
          defaultSorted = c("order"),
          columns = list(
            order = colDef(
              name = "Order",
              show = FALSE),
            column_names = colDef(
              name = "Column Name"),
            definition = colDef(
              name = "Definition")
            ))

div(class = "cpal-table",
  div(class = "cpal-header",
    h2(class = "cpal-title", "Data Dictionary for the TH Sensor")),
  tbl_datadic
)
```

```{r, Wind Defitions, echo = FALSE, message=FALSE, warning=FALSE, fig.width=12,fig.height=8, layout="l-body-outset"}
order <- c(1, 2, 3)

column_names <- c("timestamp", 
           "wind_speed_10min_average (m/s)", 
           "wind_direction_10min_average (compass degrees)") 

definition <- c("The date and time of each data point are represented every 10 minutes.", 
                "Wind speed is captured and reported in meter per second unit.",
                "Wind direction is captured and reported in compass degree unit.")

datadic_def <- data.frame(order, column_names, definition)

tbl_datadic <- reactable(datadic_def,
          compact = TRUE,
          class = "cpal-tbl",
          defaultSorted = c("order"),
          columns = list(
            order = colDef(
              name = "Order",
              show = FALSE),
            column_names = colDef(
              name = "Column Name"),
            definition = colDef(
              name = "Definition")
            ))

div(class = "cpal-table",
  div(class = "cpal-header",
    h2(class = "cpal-title", "Data Dictionary for the Anemometer Sensor")),
  tbl_datadic
)
```
